%DO NOT MESS AROUND WITH THE CODE ON THIS PAGE UNLESS YOU %REALLY KNOW WHAT YOU ARE DOING
 \chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

\noindent Coffee for some is an indispensable part of their everyday lives. There is nothing like that first sip of coffee in the morning and two new large studies confirm a few daily cups of the intense brew can be part of a healthy lifestyle. 

\noindent We conducted a qualitative research and our research objective was to determine which coffee do customers prefer more. From this research we got clear picture that consumers are drinking different types of coffee based on how their day has gone.

\noindent Each brewing device requires a unique grind size. For example, an espresso shot calls for a finer grind, while a French Press requires a courser grind. One of the major advantages of having a coffee grinder is that we could decide which coffee to have depending on our mood. There are several reasons why it is wrong to buy pre-ground coffee. Few of the problems are because the coffee oils are very delicate, which makes them an easy victim of contamination. This will contribute to your coffee tasting experience. The cells inside the roasted coffee bean contain approximately 1,000 different volatile aromas and flavours. Once ground the volatile aromas are immediately released and they react with oxygen in the air (oxidation). After 15 minutes ground coffee loses about 60 \% of its aroma. The best solution to this is always grind your coffee freshly just before brewing.

 \noindent The coffee grinder could be manual or electrically powered. One of the main benefits of an electric grinder is that they are very simple and easy to use. All you have to do is load the hopper, select your grind size, and flip the switch. In seconds you will have fresh grounds ready to be brewed. Also if you love espresso, it may be worth the extra money to buy an electric grinder. Achieving that fine espresso grind on a manual grinder is both arduous and time consuming. With some manual grinders it may take so long, that your grounds will start to go stale before you even begin to brew.

\noindent The coffee grinder could either use blades or burrs. For balanced coffee, you need uniform grounds. Blade Coffee grinders do not grind, they chop. If you put a handful of coffee beans through a blade grinder for a few seconds, you will instantly notice that the grounds are all shapes and sizes. That wont make you delicious coffee. Blade grinders have no mechanism to allow you to choose a grind size either. They are inconsistent, do not open any doors for using other brewers, and are simply a waste of money. The only good option for a coffee grinder is a burr coffee grinder. Instead of using blades to chop and spin the beans, burrs funnel beans down a narrow pathway and grind them consistently.

\noindent The purpose of this project is to design a electrical coffee grinder and manufacture a prototype of
this design.  A prototype testing will also be carried out using in-house 3D printer before the start of actual bulk production. This report gives an overview of proper planning, execution, monitoring and controlling of the project for the desired outcome.
